### 2015-03-16 bugfinding.tex
updates in bug finding section

\begin{boogie}
$p0 := $M.13;
yield;
$rv0 := $M.13;
assert $p0 == $rv0;
\end{boogie}

Our instrumentation tolerates benign races, as it will never report an assertion violation if there is a write-write race, where the two write accesses update the shared memory location with the same value.

>>>>

\begin{boogie}
$p0 := $M.13;
yield;
$rv0 := $M.13; // $rv0 is an auxiliary variable
assert $p0 == $rv0;
\end{boogie}

Our instrumentation tolerates benign races, as it will never report a write-write race, if the two write accesses update the shared memory location with the same value.
